An evaluation framework for trajectory inference methods

### 2017-11-23 analysis/paper/paper.Rmd
it's not that I don't like glue::glue, but it's one dependency less

# refering to figures & supplementary figures
refs <- tibble(ref_id = character(), name = character(), ref_type = character())
ref <- function(ref_type, ref_id, suffix="", anchor=FALSE) {
  if(nrow(refs %>% filter(ref_id == !!ref_id)) == 0) {
    refs <<- refs %>% bind_rows(tibble(
      name = create_names[[ref_type]](sum(refs$ref_type == ref_type) + 1),
      ref_type = ref_type,
      ref_id = ref_id
    ))
  }
  ref <- refs %>% filter(ref_id == !!ref_id) %>% 
    pull(name) %>% 
    {glue::glue("[**{.}{suffix}**](#{ref_type}_{ref_id})")}

  if (anchor) ref <- glue::glue("{ref}<a name='{ref_type}_{ref_id}'></a>")
  ref
}
create_names <- list(
  sfig = function(i) {glue::glue("Supplementary Figure {i}")},
  fig = function(i) {glue::glue("Figure {i}")}
)
```
# Introduction

>>>>

# refering to figures & supplementary figures
refs <- tibble(ref_id = character(), name = character(), ref_type = character())
ref <- function(ref_type, ref_id, suffix="", anchor=FALSE) {
  if(nrow(refs %>% filter(ref_id == !!ref_id)) == 0) {
    refs <<- refs %>% bind_rows(tibble(
      name = create_names[[ref_type]](sum(refs$ref_type == ref_type) + 1),
      ref_type = ref_type,
      ref_id = ref_id
    ))
  }
  ref <- refs %>% filter(ref_id == !!ref_id) %>% 
    pull(name) %>% 
    {pritt("[**{.}{suffix}**](#{ref_type}_{ref_id})")}

  if (anchor) ref <- pritt("{ref}<a name='{ref_type}_{ref_id}'></a>")
  ref
}
create_names <- list(
  sfig = function(i) {pritt("Supplementary Figure {i}")},
  fig = function(i) {pritt("Figure {i}")}
)
```
# Introduction

### 2017-11-23 analysis/paper/paper_base.Rmd
it's not that I don't like glue::glue, but it's one dependency less

# refering to figures & supplementary figures
refs <- tibble(ref_id = character(), name = character(), ref_type = character())
ref <- function(ref_type, ref_id, suffix="", anchor=FALSE) {
  if(nrow(refs %>% filter(ref_id == !!ref_id)) == 0) {
    refs <<- refs %>% bind_rows(tibble(
      name = create_names[[ref_type]](sum(refs$ref_type == ref_type) + 1),
      ref_type = ref_type,
      ref_id = ref_id
    ))
  }
  ref <- refs %>% filter(ref_id == !!ref_id) %>% 
    pull(name) %>% 
    {glue::glue("[**{.}{suffix}**](#{ref_type}_{ref_id})")}

  if (anchor) ref <- glue::glue("{ref}<a name='{ref_type}_{ref_id}'></a>")
  ref
}
create_names <- list(
  sfig = function(i) {glue::glue("Supplementary Figure {i}")},
  fig = function(i) {glue::glue("Figure {i}")}
)
```

>>>>

# refering to figures & supplementary figures
refs <- tibble(ref_id = character(), name = character(), ref_type = character())
ref <- function(ref_type, ref_id, suffix="", anchor=FALSE) {
  if(nrow(refs %>% filter(ref_id == !!ref_id)) == 0) {
    refs <<- refs %>% bind_rows(tibble(
      name = create_names[[ref_type]](sum(refs$ref_type == ref_type) + 1),
      ref_type = ref_type,
      ref_id = ref_id
    ))
  }
  ref <- refs %>% filter(ref_id == !!ref_id) %>% 
    pull(name) %>% 
    {pritt("[**{.}{suffix}**](#{ref_type}_{ref_id})")}

  if (anchor) ref <- pritt("{ref}<a name='{ref_type}_{ref_id}'></a>")
  ref
}
create_names <- list(
  sfig = function(i) {pritt("Supplementary Figure {i}")},
  fig = function(i) {pritt("Figure {i}")}
)
```
